Out-of-Sample Comparisons of Overfit Models

### 2013-12-16 paper.tex
Clean up proof of Lemma 1
This commit makes a few changes to Lemma 1 to make it easier to read; it may
fix a few minor typos as well.

For~\eqref{eq:18}, define $D_t^*$ for each $t=R+1,R+2,\dots,T-h$ so
that
\begin{equation*}
  \| D_t^* - D_t \|_2 \leq 2^{(1+\rho)/\rho} B_L \beta_{t-R}^{(\rho-2)/2\rho}
\end{equation*}
and
\begin{equation*}
  \E_R D_t^* = \E(L(y^* - x_1^{*\prime}\hat\theta_{1R}) -
  L(y^* - x_2^{*\prime}\hat\theta_{2R}) \mid \hat\theta_R) \qquad a.s.
\end{equation*}
Lemma~\ref{lem-basic-coupling} ensures that these $D_t^*$ exist.
Now,
\begin{align*}
  \Big\lVert \E_R \oosA - \E\Big(P^{-1} \sum_{t=R+1}^{T-h} D_t^* \mid
  \hat\theta_R\Big) \Big\rVert_2
  &= \Big\lVert \E_R\Big( \oosA - P^{-1} \sum_{t=R+1}^{T-h} D_t^*
  \Big) \Big\rVert_2 \\
  &= P^{-1} \sum_{t=R+1}^{T-h} \lVert D_t - D_t^* \rVert_2\\
  &= O(P^{-1}) \sum_{t=R+1}^{T-h} \beta_{t-R}^{(\rho-2)/2\rho}
\end{align*}
and this last term is $o(P^{-1/2})$ by assumption.  Essentially the
same argument proves~\eqref{eq:19} as well.

For~\eqref{eq:20}, observe that
\begin{align*}
  \|L(y^{*} -  x_i^{*\prime} \hat{\theta}_{iR}) -
  L(y^{*} - x_i^{*\prime} \hat{\theta}_{iT}) \|_1
  &\leq B_{L} \| x_i^{*\prime} (\hat{\theta}_{iR} - \hat{\theta}_{iT}) \|_2 \\
  &\leq B_{L} \big(\| x_i^{*\prime} [(X_{iT}'X_{iT})^{-1} -
  (X_{iR}'X_{iR})^{-1}] X_{iT}' \eb_{iT} \|_2 \\
  &\quad+ \| x_i^{*\prime}
  (X_{iR}'X_{iR})^{-1}[X_{iT}'\eb_{iT} - X_{iR}
  \eb_{iR} ] \|_2 \big).
\end{align*}
The first term in the upper bound satisfies
\begin{align*}
  \| x_i^{*\prime} &[(X_{iT}'X_{iT})^{-1} -
  (X_{iR}'X_{iR})^{-1}] X_{iT}' \eb_{iT} \|_2^2 =\\
  &= \E \tr\big( x_i^* x_i^{*\prime}
   [(X_{iT}'X_{iT})^{-1} - (X_{iR}'X_{iR})^{-1}] X_{iT}'\eb_{iT} \eb_{iT}X_{iT}
   [(X_{iT}'X_{iT})^{-1} - (X_{iR}'X_{iR})^{-1}] \big) \\
  &\leq \eigen_{K_i}(\E x_i x_i')
  \, \| \eigen_{K_i}(\E(X_{iT}' \eb_{iT} \eb_{iT}' X_{iT} \mid
  X_{iR}'X_{iR}, X_{iT}'X_{iT})) \|_3 \\
  & \quad \times \Big\|\sum_{j=1}^{K_i}
  \eigen_j^2((X_{iR}'X_{iR})^{-1} - (X_{iT}'X_{iT})^{-1}) \Big\|_{3/2}
\end{align*}

By Assumption~\ref{asmp-2},
\begin{equation*}
  \eigen_{K_i}(\E(X_{iT}' \eb_{iT} \eb_{iT}' X_{iT} \mid
  X_{iR}'X_{iR}, X_{iT}'X_{iT})) = O_{L_3}(T).
\end{equation*}
Also, $(X_{iR}'X_{iR})^{-1} - (X_{iT}'X_{iT})^{-1}$ has rank $P$ and
its eigenvalues are bounded by those of $(X_{iR}'X_{iR})^{-1}$, which
are $O_{L_2}(1/R)$ by Assumption~\ref{asmp-2} as well, so
\begin{align*}
  \Big\|\sum_{j=1}^{K_i}
  \eigen_j^2\big((X_{iR}'X_{iR})^{-1} - (X_{iT}'X_{iT})^{-1}\big)\Big\|_{3/2}
  &\leq \Big\|\sum_{j=K_i - P+1}^{K_i}
  \eigen_j^2\big((X_{iR}'X_{iR})^{-1} - (X_{iT}'X_{iT})^{-1}\big) \Big\|_{3/2} \\
  &= O(P/R^2)
\end{align*}
proving that
\begin{equation*}
  \| x_i^{*\prime} [(X_{iT}'X_{iT})^{-1} -
  (X_{iR}'X_{iR})^{-1}] X_{iT}' \eb_{iT} \|_2 = O(\sqrt{P/R}).
\end{equation*}

A similar argument proves that
\begin{equation*}
  \big\| x_i^{*\prime} (X_{iR}'X_{iR})^{-1}
  [X_{iT}'\eb_{iT} - X_{iR} \eb_{iR} ] \big\|_2 =  O(\sqrt{P/R}),
\end{equation*}
completing the proof.
\qed

>>>>

\begin{proof}[Proof of~\eqref{eq:18} and~\eqref{eq:19}]
For~\eqref{eq:18}, define $D_t^*$ for each $t=R+1,R+2,\dots,T-h$ so
that
\begin{equation*}
  \| D_t^* - D_t \|_2 \leq 2^{(1+\rho)/\rho} B_L \beta_{t-R}^{(\rho-2)/2\rho}
\end{equation*}
and
\begin{equation*}
  \E_R D_t^* = \E(L(y^* - x_1^{*\prime}\hat\theta_{1R}) -
  L(y^* - x_2^{*\prime}\hat\theta_{2R}) \mid \hat\theta_R) \qquad a.s.
\end{equation*}
Lemma~\ref{lem-basic-coupling} ensures that these $D_t^*$ exist.
Now,
\begin{align*}
  \Big\lVert \E_R \oosA - \E\Big(P^{-1} \sum_{t=R+1}^{T-h} D_t^* \mid
  \hat\theta_R\Big) \Big\rVert_2
  &= \Big\lVert \E_R\Big( \oosA - P^{-1} \sum_{t=R+1}^{T-h} D_t^*
  \Big) \Big\rVert_2 \\
  &\leq P^{-1} \sum_{t=R+1}^{T-h} \lVert D_t - D_t^* \rVert_2\\
  &= O(P^{-1}) \sum_{t=R+1}^{T-h} \beta_{t-R}^{(\rho-2)/2\rho}
\end{align*}
and this last term is $o(P^{-1/2})$ by assumption.

Essentially the same argument proves~\eqref{eq:19} as well.
\end{proof}

\begin{proof}[Proof of~\eqref{eq:20}]
Observe that
\begin{align*}
  \|L(y^{*} -  x_i^{*\prime} \hat{\theta}_{iR}) -
  L(y^{*} - x_i^{*\prime} \hat{\theta}_{iT}) \|_1
  &\leq B_{L} \| x_i^{*\prime} (\hat{\theta}_{iR} - \hat{\theta}_{iT}) \|_2 \\
  &\leq B_{L} \, \| x_i^{*\prime} [(X_{iT}'X_{iT})^{-1} -
  (X_{iR}'X_{iR})^{-1}] X_{iT}' \eb_{iT} \|_2 \\
  &\quad+ B_L \, \| x_i^{*\prime}
  (X_{iR}'X_{iR})^{-1}[X_{iT}'\eb_{iT} - X_{iR}
  \eb_{iR} ] \|_2 .
\end{align*}
The first term in the upper bound\,---\,$\| x_i^{*\prime}
[(X_{iT}'X_{iT})^{-1} - (X_{iR}'X_{iR})^{-1}] X_{iT}' \eb_{iT} \|_2$\,---\,satisfies
\begin{align*}
  \| x_i^{*\prime} &[(X_{iT}'X_{iT})^{-1} -
  (X_{iR}'X_{iR})^{-1}] X_{iT}' \eb_{iT} \|_2^2 =\\
  &= \E \tr\big( x_i^* x_i^{*\prime}
   [(X_{iT}'X_{iT})^{-1} - (X_{iR}'X_{iR})^{-1}] X_{iT}'\eb_{iT} \eb_{iT}X_{iT}
   [(X_{iT}'X_{iT})^{-1} - (X_{iR}'X_{iR})^{-1}] \big) \\ \label{eq:8}
  \begin{split}&\leq
    \eigen_{K_i}(\E x_i x_i')
    \, \| \eigen_{K_i}(\E(X_{iT}' \eb_{iT} \eb_{iT}' X_{iT} \mid
    X_{iR}'X_{iR}, X_{iT}'X_{iT})) \|_3 \\
    & \quad \times \Big\|\sum_{j=1}^{K_i}
    \eigen_j^2((X_{iT}'X_{iT})^{-1} - (X_{iR}'X_{iR})^{-1}) \Big\|_{3/2}
  \end{split} \\
  &= O(T) \Big\|\sum_{j=1}^{K_i}
    \eigen_j^2((X_{iT}'X_{iT})^{-1} - (X_{iR}'X_{iR})^{-1}) \Big\|_{3/2}
\end{align*}
with the second to last inequality a consequence of Holder's
inequality and the last bound holding by Assumption~\ref{asmp-2}.

Now, $(X_{iT}'X_{iT})^{-1} - (X_{iR}'X_{iR})^{-1}$ has rank $P$ and
each of its nonzero eigenvalues are bounded in absolute value by the
eivenvalues of $(X_{iR}'X_{iR})^{-1}$. The eivenvalues of
$(X_{iR}'X_{iR})^{-1}$ are $O_{L_3}(1/R)$ by Assumption~\ref{asmp-2}, so
\begin{align*}
  \Big\|\sum_{j=1}^{K_i}
  \eigen_j^2\big((X_{iR}'X_{iR})^{-1} - (X_{iT}'X_{iT})^{-1}\big)\Big\|_{3/2}
  &\leq \Big\|\sum_{j=K_i - P+1}^{K_i}
  \eigen_j^2\big((X_{iR}'X_{iR})^{-1} - (X_{iT}'X_{iT})^{-1}\big) \Big\|_{3/2} \\
  &= O(P/R^2),
\end{align*}
proving that
\begin{equation*}
  \| x_i^{*\prime} [(X_{iT}'X_{iT})^{-1} -
  (X_{iR}'X_{iR})^{-1}] X_{iT}' \eb_{iT} \|_2 = O(\sqrt{P/R}).
\end{equation*}

A similar argument proves that
\begin{equation*}
  \big\| x_i^{*\prime} (X_{iR}'X_{iR})^{-1}
  [X_{iT}'\eb_{iT} - X_{iR} \eb_{iR} ] \big\|_2 =  O(\sqrt{P/R}),
\end{equation*}
completing the proof.
\end{proof}
